SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-07-19 scipy-1.0/consortium.tex
Added author
Fix non-ASCII last name

Aditya Vijaykumar$^{30,31}$, Alessandro Pietro Bardelli$^{10}$, Alex Rothberg$^{10}$, Andreas Hilboll$^{32}$, Andreas Kloeckner$^{33}$, Anthony Scopatz$^{2}$, Antony Lee$^{34}$, Ariel Rokem$^{35}$, C. Nathan Woods$^{9}$, Chad Fulton$^{36}$, Charles Masson$^{37}$, Christian Brueffer$^{38}$, Christian H\"aggstr\"om$^{39}$, Clark Fitzgerald$^{40}$, David A. Nicholson$^{41}$, David R Hagen$^{42}$, Dmitrii V. Pasechnik$^{43}$, Emanuele Olivetti$^{44}$, Eric Martin$^{10}$, Eric Wieser$^{45}$, Fabrice Silva$^{46}$, Felix Lenders$^{47,48,49}$, Florian Wilhelm$^{50}$, G. Young$^{10}$, Gavin A. Price$^{51}$, Gert-Ludwig Ingold$^{52}$, Gregory E. Allen$^{53}$, Gregory R. Lee$^{54,55}$, Herv\'e Audren$^{56}$, Irvin Probst$^{57}$, J\"org P. Dietrich$^{58,59}$, Jacob Silterra$^{60}$, James T Webber$^{61}$, Janko Slavi\v{c}$^{62}$, Joel Nothman$^{63}$, Johannes Buchner$^{64,65}$, Johannes Kulick$^{66}$, Johannes L. Sch\"{o}nberger$^{10}$, Jos\'e Vin\'icius de Miranda Cardoso$^{67}$, Joscha Reimer$^{68}$, Joseph Harrington$^{69}$, Juan Luis Cano Rodr'iguez$^{70}$, Juan Nunez-Iglesias$^{71}$, Justin Kuczynski$^{72}$, Kevin Tritz$^{73}$, Martin Thoma$^{74}$, Matthias K\"ummerer$^{75}$, Maximilian Bolingbroke$^{76}$, Michael Tartre$^{77}$, Mikhail Pak$^{78}$, Nathaniel J. Smith$^{10}$, Nikolai Nowaczyk$^{10}$, Nikolay Shebanov$^{79}$, Oleksandr Pavlyk$^{80}$, Paul van Mulbregt$^{29}$, Per A. Brodtkorb$^{81}$, Perry Lee$^{10}$, Robert T. McGibbon$^{82}$, Roman Feldbauer$^{83}$, Sam Lewis$^{84}$, Sam Tygier$^{85}$, Scott Sievert$^{86}$, Sebastiano Vigna$^{87}$, Sourav Singh$^{88}$, Stefan Peterson$^{10}$, Surhud More$^{89,90}$, Tadeusz Pudlik$^{91}$, Takuya Oshima$^{92}$, Thomas J. Pingel$^{93}$, Thomas P. Robitaille$^{94}$, Thomas Spura$^{10}$, Thouis R. Jones$^{95}$, Tim Cera$^{10}$, Tim Leslie$^{10}$, Tiziano Zito$^{96}$, Tom Krauss$^{97}$, Utkarsh Upadhyay$^{98}$, Yaroslav O. Halchenko$^{99}$, Yoshiki V\'azquez-Baeza$^{100}$

>>>>

Aditya Vijaykumar$^{30,31}$, Alessandro Pietro Bardelli$^{10}$, Alex Rothberg$^{10}$, Andreas Hilboll$^{32}$, Andreas Kloeckner$^{33}$, Anthony Scopatz$^{2}$, Antony Lee$^{34}$, Ariel Rokem$^{35}$, C. Nathan Woods$^{9}$, Chad Fulton$^{36}$, Charles Masson$^{37}$, Christian Brueffer$^{38}$, Christian H\"aggstr\"om$^{39}$, Clark Fitzgerald$^{40}$, David A. Nicholson$^{41}$, David R Hagen$^{42}$, Dmitrii V. Pasechnik$^{43}$, Emanuele Olivetti$^{44}$, Eric Martin$^{10}$, Eric Wieser$^{45}$, Fabrice Silva$^{46}$, Felix Lenders$^{47,48,49}$, Florian Wilhelm$^{50}$, G. Young$^{10}$, Gavin A. Price$^{51}$, Gert-Ludwig Ingold$^{52}$, Gregory E. Allen$^{53}$, Gregory R. Lee$^{54,55}$, Herv\'e Audren$^{56}$, Irvin Probst$^{57}$, J\"org P. Dietrich$^{58,59}$, Jacob Silterra$^{60}$, James T Webber$^{61}$, Janko Slavi\v{c}$^{62}$, Joel Nothman$^{63}$, Johannes Buchner$^{64,65}$, Johannes Kulick$^{66}$, Johannes L. Sch\"{o}nberger$^{10}$, Jos\'e Vin\'icius de Miranda Cardoso$^{67}$, Joscha Reimer$^{68}$, Joseph Harrington$^{69}$, Juan Luis Cano Rodr\'iguez$^{70}$, Juan Nunez-Iglesias$^{71}$, Justin Kuczynski$^{72}$, Kevin Tritz$^{73}$, Martin Thoma$^{74}$, Matthias K\"ummerer$^{75}$, Maximilian Bolingbroke$^{76}$, Michael Tartre$^{77}$, Mikhail Pak$^{78}$, Nathaniel J. Smith$^{10}$, Nikolai Nowaczyk$^{10}$, Nikolay Shebanov$^{79}$, Oleksandr Pavlyk$^{80}$, Per A. Brodtkorb$^{81}$, Perry Lee$^{10}$, Robert T. McGibbon$^{82}$, Roman Feldbauer$^{83}$, Sam Lewis$^{84}$, Sam Tygier$^{85}$, Scott Sievert$^{86}$, Sebastiano Vigna$^{87}$, Sourav Singh$^{88}$, Stefan Peterson$^{10}$, Surhud More$^{89,90}$, Tadeusz Pudlik$^{91}$, Takuya Oshima$^{92}$, Thomas J. Pingel$^{93}$, Thomas P. Robitaille$^{94}$, Thomas Spura$^{10}$, Thouis R. Jones$^{95}$, Tim Cera$^{10}$, Tim Leslie$^{10}$, Tiziano Zito$^{96}$, Tom Krauss$^{97}$, Utkarsh Upadhyay$^{98}$, Yaroslav O. Halchenko$^{99}$, Yoshiki V\'azquez-Baeza$^{100}$
